Behavior Driven Development in Haskell

### 2012-06-01 paper.tex
Semantic fix
Wording

SmallCheck~\cite{smallcheck} is a tool for
automatic exhaustive testing at a certain level.
Both Doctest and Hspec do not have support for SmallCheck
at this moment.
Hspec's mechanism for evidence is extensible.
If necessary, it would be easy to support SmallCheck.

>>>>

SmallCheck~\cite{smallcheck} is a tool for
automatic exhaustive testing up to a certain depth.
Both Doctest and Hspec do not have support for SmallCheck
at this moment.
Hspec's mechanism for evidence is extensible, and it would be easy to
add support for SmallCheck.
